% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{enumitem}
\usepackage{fancyhdr}
\robustify\cftdotfill


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup

\setlength{\headheight}{14pt}
\setlength{\headsep}{0in}
% \setlength{\evensidemargin}{-0.5in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7.5in}
\setlength{\topmargin}{-0.75in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
% \setlist[itemize, 1]{leftmargin=0in}
% \setlist[itemize]{leftmargin=.5in}
\setitemize{topsep=6pt, leftmargin=.25in}

%-----------------------------------------------------------
% Header & Footer
\pagestyle{fancy}
% disable header rule (horizontal line)
\renewcommand{\headrulewidth}{0pt}
% enable header rule
\renewcommand{\footrulewidth}{0.4pt}
\lfoot{\emph{\footnotesize{This resumé contains clickable links. View in your web browser for the full experience.}}}
\cfoot{}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\renewcommand{\labelitemi}{•}
\renewcommand{\labelitemii}{◦}
\renewcommand{\labelitemiii}{$\ast$}
\newcommand{\resheading}[1]{\vspace{6pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[7.25in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.25in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Tim Etchells} & \textbf{\today} \\
Software Developer & tetchel@gmail.com \\
\uline{\href{https://github.com/tetchel}{https://github.com/tetchel}} & \uline{\href{https://www.linkedin.com/in/tim-etchells-a235b513b/}{LinkedIn}} \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{EXPERIENCE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

 \item
	\ressubheading{IBM - \uline{\href{https://codewind.dev}{Codewind}}}{Toronto, ON}{Staff Software Developer}{July 2018 - Present}
	\begin{itemize}
    \item{Author of \uline{\href{https://marketplace.visualstudio.com/items?itemName=IBM.codewind}{Codewind for VS Code}},\
      an extension to facilitate cloud-native, containerized development.
    }
    \item{Responsible for a wide variety of duties including planning, designing, developing, testing, implementing continuous integration, publishing, writing documentation, and providing support to users.}
    \item{See \uline{\href{https://github.com/eclipse/codewind-vscode}{https://github.com/eclipse/codewind-vscode}} for source code\
      and \uline{\href{https://github.com/eclipse/codewind-vscode/pulls?q=is\%3Apr+author\%3Atetchel}{pull requests}}.\
    }
    \item{Also refer to \uline{\href{https://github.com/eclipse/codewind/issues?q=is\%3Aissue+author\%3Atetchel}{issues I opened}}, and\
      \uline{\href{https://github.com/eclipse/codewind/issues?q=is\%3Aissue+commenter\%3Atetchel}{issues I participated in.}}
    }
	\end{itemize}

\item
	\ressubheading{IBM - WebSphere Developer Tools for Eclipse}{Toronto, ON}{Software Development Intern}{May 2016 - Aug. 2017}
	\begin{itemize}
    \resitem{Identified and fixed defects, usability problems, and automated test issues.}
    \resitem{Designed and implemented a continuous integration build system for the \uline{\href{https://github.com/OpenLiberty/open-liberty-tools}{OpenLibertyTools}}.}
	\end{itemize}

\item
  \ressubheading{Personal Projects}{}{Refer to my GitHub for more examples of my work.}{}
  \begin{itemize}
    \resitem{\uline{\href{https://github.com/tetchel/shexter}{shexter}} and \uline{\href{https://github.com/tetchel/shexter-client}{shexter-client}}
      - Send and receive texts in your command-line using only your local area network. Built with Android (Java), Python. }

    \resitem{\uline{\href{https://github.com/nwam/fradio-server}{fradio}} and \uline{\href{https://github.com/tetchel/fradio-client}{fradio-client}}
      - Synchronize your Spotify with your friends' to hear the same music as they do, in real time. Built with Flask (Python), Android (Java), MySQL. }

    \resitem{\uline{\href{https://github.com/tetchel/slack-explorer}{slack-explorer}}
      - Create a live, interactive network graph and other visualizations of your Slack workspace's channels and group messages. Built with TypeScript, Express.js, Mongo. }
  \end{itemize}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{SKILLS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item{\textbf{Languages:} Strong TypeScript/JavaScript, Java. Intermediate Python, C\#, Bash, HTML/CSS, SQL.}
  \item{\textbf{Tools:} VS Code, Eclipse, git/GitHub, npm, Travis, Jenkins, Express.js, Mocha.js, JUnit, webpack.}
  \item{\textbf{Runtimes \& Platforms:} Node.js, Android, Docker, Kubernetes, Unity, Linux, macOS, Windows.}
  \item{\textbf{Paradigms:} Backend development, IDE extensions, REST, open source, agile project management, continuous integration, test automation, workflow automation.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{EDUCATION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item

  \ressubheading{Western University}{London, ON}{Bachelor of Science}{April 2018}
  \begin{itemize}
      \item{Honors Specialization in Computer Science, Minor in Software Engineering}
      % \begin{itemize}
        \item Together, this specialization and minor are {\uline{\href{https://www.westerncalendar.uwo.ca/Archive/2017/2017/pg655.html}{accredited by CSAC}}} as a Software Engineering degree.
      % \end{itemize}
      \item{3.9 GPA in Computer Science and Math courses}
      \item{Dean's Honor List last three years of study}
	\end{itemize}

\end{itemize}

\end{document}
